\begin{problem}{Minimize Sum}{standard input}{standard output}{1 second}{256 megabytes}

Given an array $a$ of $n$ integers, find the minimum sum of the array after removing two elements of $a$ and appending their \href{https://en.wikipedia.org/wiki/Bitwise_operation#XOR}{bitwise XOR} to the array.

\InputFile
Each test contains multiple test cases. The first line of input contains a single integer $t$ ($1 \le t \le 100$) "--- the number of test cases.

The first line of each test case contains a single integer $n$ ($2 \le n \le 2 \cdot 10^5$) "--- the length of the array $a$.

The second line of each test case contains $n$ integers $a_1,a_2, \ldots ,a_n$ ($1 \le a_i \le 10^9$) "--- the elements of the array $a$.

It is guaranteed that the sum of $n$ over all test cases does not exceed $2 \cdot 10^5$.

---

Tests in subtasks are numbered from $1 - 20$ with samples skipped. Each test is worth $\frac{100}{20}=5$ points.


Tests $1 - 5$ will satisfy $t \le 10$, $n \le 1000$.

The remaining tests do not satisfy any additional constraints.

\OutputFile
For each test case, output a single integer "--- the minimum achievable sum.

\Example

\begin{example}
\exmpfile{example.01}{example.01.a}%
\end{example}

\Note
In the first test case of the sample test, it is optimal to choose the elements $2$ and $3$, deleting them and appending $1$ to the array. This produces a new sum of $8$.

In the second test case of the sample test, it is optimal to choose the elements $1$ and $9$, deleting them and appending $8$ to the array. This produces a new sum of $12$.

---

Problem Idea: xug

Problem Preparation: xug

Occurrences: Novice E

\end{problem}

