\begin{problem}{Monkey Arrays}{standard input}{standard output}{1 second}{256 megabytes}

Yash really likes monkeys and special arrays. Because he was curious, Curios George gave Yash an array $A$ of length $N$, and now Yash wonders how many \textit{good} subarrays exist in this array.

Specifically, Yash deems a subarray \textit{good} if $X$, his favorite number, is the maximum value in the subarray, $Y$, his second favorite number, is the minimum in the subarray, and $K$, his least favorite number, is not in the subarray. In other words, in a given subarray, $X$ should be the maximum value, $Y$ should be the minimum, and $K$ should not be in the subarray.

\InputFile
Each test contains multiple test cases. The first line of input contains a single integer $t$ $(1 \leq t \leq 5 \cdot 10^4)$ "--- the number of test cases.

The first line of each test case contains four integers $N$, $X$, $Y$, and $K$ ($1 \le N \le 5 \cdot 10^5, 1 \le Y < K < X \le 10^9$).

The second line of each test case contains $N$ integers $A_1,A_2,\ldots,A_N$ ($1 \le A_i \le 10^9$) "--- the elements of the array $A$.

It is guaranteed that the sum of $N$ over all test cases does not exceed $5 \cdot 10^5$.

---

Tests in subtasks are numbered from $1-20$ with samples skipped. Each test is worth $\frac{100}{20}=5$ points.

Tests $1-5$ satisfy that the sum of $N$ over all test cases does not exceed $100$.

Tests $6-10$ satisfy that the sum of $N$ over all test cases does not exceed $1000$.

The remaining tests do not satisfy any additional constraints.

\OutputFile
For each test case, output a single integer "--- the number of \textit{good} subarrays in the array $A$.

\Example

\begin{example}
\exmpfile{example.01}{example.01.a}%
\end{example}

\Note
In the first test case of the sample test, the $5$ subarrays that are \textit{good} are $[6, 7, 4]$, $[6, 7, 4, 6]$, $[7, 4]$, $[7, 4, 6]$, and $[4, 6, 7]$.

In the second test case of the sample test, there are no \textit{good} subarrays.

---

Problem Idea: yash_9a3b

Problem Preparation: yash_9a3b, xug

Occurrences: Novice G, Advanced B

\end{problem}

